---
title: "Begining Machine Learning with R"
output: R machine Learning 
---


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}
library(xgboost)
library(tidyverse)
```
```{r}
install.packages("tidyverse")
```


```{r}
library("ggplot2")
library("ggthemes")
library("psych")
library("relaimpo")
```


```{r}
insurance = read.csv("insurance.csv")
```


```{r}
head(insurance,n=5)
```


```{r}
summary(insurance)
```


```{r}
describeBy(insurance$charges,insurance$region)
```


```{r}
describeBy(insurance$charges,insurance$sex)

```


```{r}
ggplot(data =insurance , aes(region,charges))+geom_boxplot(fill = c(2:5))+theme_classic()+ggtitle("Boxplot of Medical")
```


```{r}
pairs.panels(insurance[c("age", "children", "charges")])
```


```{r}
ins_model = lm
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

